Re-finding to support a Deep Web Question Answering System

### 2010-03-04 trunk/paper/semsearch10/content/ontological_realms.tex
third round of changes by jnw

\subsection{Class Heterarchy} 
% Author: Clint 
Since, our representation of semi structured query [citation needed] is in OWL ontology format, and our aim is to compare and rank the queries in this format, we had to define a similarity measure between ontologies. The defined ontology class comparison measure "class divergence" [citation needed] assumes that we have an ontology store with unambiguous interpretation of classes and strict hierarchical subclass super class relationships and the classes to be compared should belong to it. We cannot find any robust existing ontology library of that nature for this purpose. So we decided to build a new ontology store and as an initial step the categories from DBPedia store [citation needed] are used. Even though, some of these categories are loosely coupled and not fully agreed upon the sub category and super category relationships, this DBPedia has enormous amount of data in linked form [citation needed]. The OWL ontology [citation needed] format is followed in this process. The DBPedia categories are converted into OWL ontology classes and the super class - sub class relationships are built using the OWL super class sub class axioms [citation needed]. Another reason for selecting OWL for this purpose is that we can make use of the existing APIs for building and reasoning [citation needed] the ontology relationships.

@@

\subsection{Associating Terms with Categories}
%joir-dan

Building Ontological Realms

Once the semantic hierarchy is created, the next step is to create training data for the system. The task is then to grab the pages, build a corpus relating to a given category, and then compile the information in a meaningful way. The overall goal is to grab enough information to properly characterize a category while limiting the amount of unnecessary content within the corpus. The problem with this approach is the page density varies greatly across the heterarchy. Each category within the DBpedia/Wikipedia heterarchy contains a set of information pages, P, that correspond to concepts that share said category. Considering that the categorical structure is a directed acyclic graph  \cite{Suchanek07yago:a}, we consider the use of a Markov Blanket \cite{Friedman97bayesiannetwork} in describing a particular category. The assumption is that a node can be fully described by its ancestor, descendant, and spousal nodes (parent node of subcategory not equal to the category). While this does not completely solve the issue of a category residing in a sparse area of the graph, the amount of information that can be obtained per blanket is usually more helpful than per category.

Consider the abbreviated Markov blanket for the category Automobiles:

% figure: abbreviated Markov blanket for the category Basketball  
\begin{figure}[t]
\centering
\includegraphics[width=90mm]{BlanketExample.eps}
\caption{Abbreviated Markov blanket for the category Automobiles}
\label{fig:abbrv_bb_blanket}
\end{figure}

The subcategories of the category Automobiles (… Driving, Traffic Law, Automobiles by Decade, Auto Racing…) can be seen as grabbing information specific to the category. The supercategories (Road Vehicles) place the category in a higher perspective, abstractly describing basketball as a concept. The spousal categories (...Motorsport, Individual Sport...) are an abstract description of the subcategories.

@@

\begin{lstlisting}[language=Python,frame=single,tabsize=2,caption=BlanketSubjectRetreival, label=BlanketSubjectRetreival]
def BlanketSubjectRetreival(blanket, maxLevel):
	for category in blanket:
		subjectSet.add(grabsubjects(category))
		diff = afterSize - beforeSize
		if diff <= a and category is subcategory:
			PlusOneMechanism(category, maxLevel)
	return subjectSet
\end{lstlisting}

\begin{lstlisting}[language=Python,frame=single,tabsize=2,caption=PlusOneMechanism, label=PlusOneMechanism]
def PlusOneMechanism(category, level):
	plusOneSet = grabPlusOneSubcategories(category)
	for subcategory in plusOneSet:
		subject.add(grabSubjects(subcategory))
		diff = afterSize - beforeSize
		if diff <= a and level > 0:
			PlusOneMechanism(subcategory, level-1)

>>>>

\subsection{Category Heterarchy} 
% Author: Clint 
Since, our representation of semi structured query [citation needed]
is in OWL ontology format, and our aim is to compare and rank the
queries in this format, we had to define a similarity measure between
ontologies. The defined ontology class comparison measure "class
divergence" [citation needed] assumes that we have an ontology store
with unambiguous interpretation of classes and strict hierarchical
subclass super class relationships and the classes to be compared
should belong to it. We cannot find any robust existing ontology
library of that nature for this purpose. So we decided to build a new
ontology store and as an initial step the categories from DBPedia
store [citation needed] are used. Even though, some of these
categories are loosely coupled and not fully agreed upon the sub
category and super category relationships, this DBPedia has enormous
amount of data in linked form [citation needed]. The OWL ontology
[citation needed] format is followed in this process. The DBPedia
categories are converted into OWL ontology classes and the super class
- sub class relationships are built using the OWL super class sub
class axioms [citation needed]. Another reason for selecting OWL for
this purpose is that we can make use of the existing APIs for building
and reasoning [citation needed] the ontology relationships.

@@

\subsection{Associating Terms with Categories} %joir-dan The
subcategories of the category Automobiles (… Driving, Traffic Law,
Automobiles by Decade, Auto Racing…) can be seen as grabbing
information specific to the category. The supercategories (Road
Vehicles) place the category in a higher perspective, abstractly
describing basketball as a concept. The spousal categories
(...Motorsport, Individual Sport...) are an abstract description of
the subcategories.

@@

\begin{lstlisting}[language=Python,frame=none,tabsize=2,caption=BlanketSubjectRetreival,label=BlanketSubjectRetreival,basicstyle=\small]
def BlanketSubjectRetreival(blanket, maxLevel):
	for category in blanket:
		subjectSet.add(grabsubjects(category))
		diff = afterSize - beforeSize
		if diff <= a and category is subcategory:
			PlusOneMechanism(category, maxLevel)
	return subjectSet
\end{lstlisting}

\begin{lstlisting}[language=Python,frame=none,tabsize=2,caption=PlusOneMechanism, label=PlusOneMechanism,basicstyle=\small]
def PlusOneMechanism(category, level):
	plusOneSet = grabPlusOneSubcategories(category)
	for subcategory in plusOneSet:
		subject.add(grabSubjects(subcategory))
		diff = afterSize - beforeSize
		if diff <= a and level > 0:
			PlusOneMechanism(subcategory, level-1)

### 2010-03-04 trunk/paper/semsearch10/content/qrr.tex
third round of changes by jnw

\subsection{Query Resolution Recorder}
% Chris
Answering a question using the deep web requires one to navigate through a sequence of one or more web pages and links.  Many of the accesses involve clicks through web forms to resulting pages.  We have developed a model that represents the various actions a user may carry out during this process.  We record the user actions with a browser plugin called the \emph{query resolution recorder} (QRR).

@@

Any discovery process  consists of a sequence of these transactions.  Additionally, data collected for inputs and outputs may be found during any stage of the complete discovery process.  An output collected during one stage of an extraction may be the input to a subsequent stage in the extraction.  The QRR builds the completed user collection process into a QRM.  The following is a mathematical formulation of information collected for user web interactions.\\

@@

\item $\Upsilon$ is the sequence of input classes $\left< \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4} \right>$ where $\Upsilon_{1}$ represents the \emph{who} context of the associated query, $\Upsilon_{2}$ represents the \emph{what} context, $\Upsilon_{3}$ represents the \emph{when} context, and $\Upsilon_{4}$ represents the \emph{where} context.

\item $\Omega$ is the sequence of output classes $\left<\Omega_{1}, \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where $\Omega_{1}$ represents the \emph{who} context of the associated query, $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$ represents the \emph{when} context, and $\Omega_{4}$ represents the \emph{where} context.

@@

\subsection{Generalization}
% Christan
The response pages created by querying web forms are dynamically generated with a templated structure. This generalization per page is done using the GenPath algorithm developed by Badica et al. \cite{Badica06}. Additionally, the community may be able to answer a particular SSQ using many different page interactions. Therefore, we proposed a method of generalizing extraction path to a result across pages. This method removes unnecessary page interactions and finds the shortest path to the result pages.

The websites that are wrapped are highly susceptible to structural changes \cite{TanZMG07}. Generalizing the extraction paths help to overcome small structural changes. If a website changes to the point where a QRM is no longer useful, the QRM not considered fresh. Morpheus allows users to rate the freshness of QRMs.

>>>>

\section{Query Resolution Recorder (QRR)}
\label{sec:qrr}
% Chris
Answering a question using the deep web requires one to navigate
through a sequence of one or more web pages and links.  Many of the
accesses involve clicks through web forms to resulting pages.  We have
developed a model that represents the various actions a user may carry
out during this process.

@@

Any discovery process consists of a sequence of these transactions.
Additionally, data collected for inputs and outputs may be found
during any stage of the complete discovery process.  An output
collected during one stage of an extraction may be the input to a
subsequent stage in the extraction.  The QRR builds the completed user
collection process into a QRM.  The following is a mathematical
formulation of information collected for user web interactions.

@@

\item $\Upsilon$ is the sequence of input categories $\left<
  \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4} \right>$
  where $\Upsilon_{1}$ represents the \emph{who} context of the
  associated query, $\Upsilon_{2}$ represents the \emph{what} context,
  $\Upsilon_{3}$ represents the \emph{when} context, and
  $\Upsilon_{4}$ represents the \emph{where} context.

\item $\Omega$ is the sequence of output categories $\left<\Omega_{1},
  \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where $\Omega_{1}$
  represents the \emph{who} context of the associated query,
  $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$
  represents the \emph{when} context, and $\Omega_{4}$ represents the
  \emph{where} context.

@@

%\subsection{Generalization}
% Christan
The response pages created by querying web forms are dynamically
generated with a templated structure. This generalization per page is
done using the GenPath algorithm developed by Badica et
al. \cite{Badica06}. Additionally, the community may be able to answer
a particular SSQ using many different page interactions. Therefore, we
use a method of generalizing extraction path to a result across
pages. This method removes unnecessary page interactions and finds the
shortest path to the result pages.

Websites wrapped by a system such as this are highly susceptible to
structural changes \cite{TanZMG07}. Generalizing the extraction paths
helps overcome small structural changes. If a website changes to the
point where a QRM is no longer useful, the QRM is not considered
fresh. User ratings of QRM freshness can be employed in the SSQ matching
process detailed in Section \ref{sec:ssq}.
